\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-14 public/paper/pyg4ometry.tex
is -> are
replace words "typically" (used too many times in this paragraph)

%% main text
\section{Introduction} \label{sec:introduction}
There are numerous different software codes to simulate the passage of particles through material radiation transport (RT) programmes these 
include MCNP \cite{Mcnp_Werner}, FLUKA \cite{Fluka_Ferrari,Fluka_Bohlen}, Geant3 \cite{Geant3_Brun} and Geant4 \cite{Geant4_Agostinelli}. 
All these codes are based on the Monte Carlo technique but each code either has a particular specialism, simulation methodology or target user community.  
RT Monte Carlo (RTMC) simulations have diverse uses including shielding calculations for radiological protection, detector performance, medical imaging and therapy and space radiation environment  simulation are some examples. A fundamental requirement of all of the codes is to supply a computer-readable description of the 
physical three-dimensional geometry that  the particles are passing through.  The creation of geometry files is typically a very time-consuming 
activity and the simulation validity and performance is directly dependent on the quality of the geometry. There is no standard geometry format used across MCRT 
codes, with each MCRT code typically using its own unique format. The requirement of a geometry system that allows the conversion between files prepared for different 
codes will enable cross-checks of the physics processes in different particle transport codes. Typically an MCRT code user will not have geometry in FLUKA 
and Geant4 for example. The file formats used for geometry are typically focused on the computational efficiency of a particle tracking task and not ease of use of a user. In addition to the creation of geometry files for RT programs, usually computer-aided design (CAD) files exist for systems which 
need to be simulated. The fundamental geometric representations in CAD files is typically not amenable for MCRT programs.  For these reasons it is 
advantageous to create a software tool that allows particle transport code users to rapidly develop error-free geometry files, convert between common MCRT 
program geometry formats and finally import CAD models.

>>>>

%% main text
\section{Introduction} \label{sec:introduction}
There are numerous different software codes to simulate the passage of particles through material radiation transport (RT) programmes these 
include MCNP \cite{Mcnp_Werner}, FLUKA \cite{Fluka_Ferrari,Fluka_Bohlen}, Geant3 \cite{Geant3_Brun} and Geant4 \cite{Geant4_Agostinelli}. 
All these codes are based on the Monte Carlo technique but each code either has a particular specialism, simulation methodology or target user community.  
RT Monte Carlo (RTMC) simulations have diverse uses including shielding calculations for radiological protection, detector performance, medical imaging and therapy and space radiation environment  simulation are some examples. A fundamental requirement of all of the codes is to supply a computer-readable description of the 
physical three-dimensional geometry that  the particles are passing through.  The creation of geometry files is typically a very time-consuming 
activity and the simulation validity and performance is directly dependent on the quality of the geometry. There is no standard geometry format used across MCRT 
codes, with each MCRT code typically using its own unique format. The requirement of a geometry system that allows the conversion between files prepared for different 
codes will enable cross-checks of the physics processes in different particle transport codes. Typically an MCRT code user will not have geometry in FLUKA 
and Geant4 for example. The file formats used for geometry are generally focused on the computational efficiency of a particle tracking task and not ease of use of a user. In addition to the creation of geometry files for RT programs, usually computer-aided design (CAD) files exist for systems which 
need to be simulated. The fundamental geometric representations in CAD files are usually not amenable for MCRT programs.  For these reasons it is 
advantageous to create a software tool that allows particle transport code users to rapidly develop error-free geometry files, convert between common MCRT 
program geometry formats and finally import CAD models.
